Solar jet observed at the limb in SDO/SST

### 2016-05-25 paper/ms_temp_paper.tex
Instability section

A third  category are coronal jets, observed in slightly hotter lines of $17.1$ but still EUV such as those discussed in \cite{Shibata1992}.
Here, they are described later in \cite{Shibata1994} as reconnection events, where reconnection is triggered by flux emergence at the base of a small scale loop.
However, after this reconnection, there are several models as to how the system will evolve.
\cite{Moore2010} demonstrate a dichotomy in formation mechanism of coronal jets, between the standard 'inverted Y' model demonstrated by Shibata and the blowout jet model. 
This model differs from the standard model, in this case the reconnection leads to a 'curtain' of plasma flow as opposed to the 'spire' from the standard model.
The difference between the two models originates in initial configuration of the overlying arch. 
In standard jets the arch has no appreciable shear, whereas for a blowout jet the arch is twisted and sheared sufficiently to drive the explosive outflow which forms the jet.
Coronal jets have also been shown to accelerate particles into interplanetary space \citep{Li2011}, there is also evidence for repeat onset jets, with several re-occurrences, see \cite{Li2011} and \cite{Chifor2008} demonstrate repeat on-set of jets driven by flux cancellation.

@@

\section{Temperature Maps}
\label{temp_map_sect}

>>>>

A third  category are coronal jets, observed in slightly hotter lines of $17.1$ but still EUV such as those discussed in \cite{Shibata1992} and simulated in papers such as \cite{Wyper2016}.
Here, they are described later in \cite{Shibata1994} as reconnection events, where reconnection is triggered by flux emergence at the base of a small scale loop.
However, after this reconnection, there are several models as to how the system will evolve.
\cite{Moore2010} demonstrate a dichotomy in formation mechanism of coronal jets, between the standard 'inverted Y' model demonstrated by Shibata and the blowout jet model. 
This model differs from the standard model, in this case the reconnection leads to a 'curtain' of plasma flow as opposed to the 'spire' from the standard model.
The difference between the two models originates in initial configuration of the overlying arch. 
In standard jets the arch has no appreciable shear, whereas for a blowout jet the arch is twisted and sheared sufficiently to drive the explosive outflow which forms the jet.
Coronal jets have also been shown to accelerate particles into interplanetary space \citep{Li2011}, there is also evidence for repeat onset jets, with several re-occurrences, see \cite{Li2011} and \cite{Chifor2008} demonstrate repeat on-set of jets driven by flux cancellation.

@@

\section{Effect on the atmosphere}
\label{temp_map_sect}

With the increased resolution we can visually inspect the boundary between the jet and atmosphere.
\cref{multi_db} details the evolution of the jet in the core of H$\alpha$ in over $115$ seconds.
At the boundary we observe narrow dark columns in the emission on either side of the jet.
Given that they appear on either side of the jet column and that the observations are in the core of the $H\alpha$ line, it is unlikely that this would be caused by a doppler-like effect.
One possibility is that the cause is an instability effect, such as shear or Kelvin-Helmholtz, seen in \cite{Zaqarashvili2014} as the jet moves throughout the higher atmosphere.
Supporting this hypothesis is that these images were recorded in the 'second phase' of the jet \emph{i.e.} after the second reconnection and the jet extends to its peak in $30.4$ nm. 
As such, it is possible that these columns are a result of plasma being accelerated into the atmosphere.
